Sr: Processing Data Streams and Avoiding Work

### 2012-05-04 paper/paper.tex
Add discussion section

\usepackage{fullpage}
\usepackage{listings}
\usepackage{graphicx}
\graphicspath{{images/}}
\usepackage{tabularx}

@@

\section{Introduction}
\label{sec:intro}
One of the fundamental problems MapReduce was created to solve was processing
the growing amount of data in the world. Now with the open source Apache Hadoop
and Pig, it is easy to process and query the terabytes of data an organization
may collect. With terabytes of data, however, it is scarcely necessary to examine
every entry to uncover trends. Google runs PageRank on the entire Internet, but if
it only did on half of the pages it crawls, it would likely still have a usable
index for delivering the first 5 pages of results.

@@

The remainder of this paper is organized as follows. Section~\ref{sec:relwork} provides
an overview of related work on distributed stream processing as well as dynamic and
approximate computations. Section~\ref{sec:design} details how I designed Sr.
Section~\ref{sec:methodology} explains the methodology used to perform a cvase study
using Sr. Section~\ref{sec:evaluation} evaluates the effectiveness of Sr in the case study.

@@

Collectors also expose an API endpoint for accessing the results of a job. This endpoint
can be used by another spout to chain Sr jobs together.
\subsection{Master}
There is one master node per Sr network. It has a function similar to the jobtracker in
MapReduce. New jobs are scheduled with the master and it initializes other nodes in the
cluster with job state. For each job, the master schedules roles among nodes in a round robin
manner to minimize the total number of outstanding roles on any one node.

@@

Another consequence of the master being the only well-known node is that all data in the
cluster must flow through it. The master maintains two queues per job for buffering job
progress from fetchers and workers and periodically pushes this state out to workers and
collectors, respectively.
\subsection{Configuring a Cluster for a Job}
Apart from spouts, all nodes in a cluster modify their behavior based on the job they are
running. The master must know the appropriate number of nodes to spin up; fetchers need to
know how to talk to spouts; workers need to know how to compute results; and collectors need
to know how to combine batched worker results.

@@

The results of the word count job are then used in a script to compute the top 100 words.
The cluster and word count job could be used in a two-stage top-k job. This script filters
out SEO stopwords [stopword] to achieve more interesting results.

@@

\section{Discussion}
\label{sec:discussion}

\bibliography{sr}{}
\bibliographystyle{plain}

>>>>

\usepackage{fullpage}
\usepackage{listings}
\usepackage{graphicx}
\graphicspath{{images/}}
\usepackage{tabularx}
\usepackage{url}

@@

\section{Introduction}
\label{sec:intro}
One of the fundamental problems MapReduce was created to solve was processing
the growing amount of data in the world. Now with the open source Apache Hadoop
and Pig~\cite{piglatin}, it is easy to process and query the terabytes of data an organization
may collect. With terabytes of data, however, it is scarcely necessary to examine
every entry to uncover trends. Google runs PageRank on the entire Internet, but if
it only did on half of the pages it crawls, it would likely still have a usable
index for delivering the first 5 pages of results.

@@

The remainder of this paper is organized as follows. Section~\ref{sec:relwork} provides
an overview of related work on distributed stream processing as well as dynamic and
approximate computations. Section~\ref{sec:design} details how I designed Sr.
Section~\ref{sec:methodology} explains the methodology used to perform a cvase study
using Sr. Section~\ref{sec:evaluation} evaluates the effectiveness of Sr in the case study.
Section~\ref{sec:discussion} enumerates issues with Sr's current implementation.

@@

Collectors also expose an API endpoint for accessing the results of a job. This endpoint
can be used by another spout to chain Sr jobs together.
\subsection{Master}
\label{sec:master}
There is one master node per Sr network. It has a function similar to the jobtracker in
MapReduce. New jobs are scheduled with the master and it initializes other nodes in the
cluster with job state. For each job, the master schedules roles among nodes in a round robin
manner to minimize the total number of outstanding roles on any one node.

@@

Another consequence of the master being the only well-known node is that all data in the
cluster must flow through it. The master maintains two queues per job for buffering job
progress from fetchers and workers and periodically pushes this state out to workers and
collectors, respectively.
\subsection{Configuring a Cluster for a Job}
\label{sec:jobfile}
Apart from spouts, all nodes in a cluster modify their behavior based on the job they are
running. The master must know the appropriate number of nodes to spin up; fetchers need to
know how to talk to spouts; workers need to know how to compute results; and collectors need
to know how to combine batched worker results.

@@

The results of the word count job are then used in a script to compute the top 100 words.
The cluster and word count job could be used in a two-stage top-k job. This script filters
out SEO stopwords~\cite{stopwords} to achieve more interesting results.

@@

\section{Implementation Notes}
\label{sec:discussion}
This section describes deficiencies in the implementation of Sr used to run the case study
in this paper and goals for the next version of the system.

\subsection{On-the-Fly Job Reconfiguration}
The mechanism for altering execution of a job as it is running described in Section~\ref{sec:jobfile}
is not yet implemented. Adding this feature to Sr is a matter of adding an API endpoint
to the servers run by each role and adding a bin-script to submit the new Jobfile.

\subsection{Internode Communication}
In Section~\ref{sec:master} I mentioned design difficulties relating to the master and using HTTP
servers for sending messages between nodes. I initially chose to use HTTP requests with POST payloads
to send data and results between nodes because of its low barrier to entry; however, initiating many
HTTP requests in succession is expensive. When killing jobs on worker nodes, the observed time savings
was minimal because most of the time spent per datum involved shipping it from the master to the worker.

In order to mitigate the effects of this problem, I batched individual requests into groups of 5. This
lowered the number of connections I was initiating but it also limited the parallelism of the cluster
and removed workers from the pool for longer periods because they had more data to process at a time.
A killed task on the worker no longer freed it up to receive a new task immediately.
Keeping workers removed from the pool caused the queues on the master to grow longer as the workers
could no longer keep up with the rate the fetcher was producing data.

Eventually, I introduced a configuration option to kill tasks at the master. The master then
decides to discard a task as it is popped from the queue, before it is ever sent to a worker.
Doing so improved the execution time of the cluster but also meant that workers no longer had
a full idea of how accurate they were being because they never killed any tasks themselves.

In order to address this problem, the master needs to keep a persistent channel open between
it and all active nodes. Communication channels should be established when nodes come online.
Possible solutions include writing to a socket or using a higher abstraction like AMPQ. AMPQ
is appealing because it relieves the master from handling queues.

\subsection{Node Health}
Currently, the master does not probe nodes to ensure that they are responsive. In the case that
a node is serving a worker role for a job, this deficiency is masked. The node will simply not
return the HTTP request sent to it to push it some data and the worker will remain removed from
the pool. If the node is in the role of fetcher or collector, the master will stall.

All messages passed by the master to other nodes must be made non-blocking.

\subsection{Job Management}
There is no support for killing jobs or removing them from the master's data structures. The only
way to remove a job is to kill the master and all other nodes in the cluster.

\bibliography{paper}{}
\bibliographystyle{plain}
